Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.4]

### 2017-02-28 QPQ9/qpq9_draft.tex
Calculate scatters in bootstrap with Gaussian fitting

\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.2]}

@@

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large intrinsic velocity fields, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue the results can be 
explained by outflowing gas combined with anisotropic or intermittent ionizing radiation of the 
quasars. 
\end{abstract}

@@

\begin{figure*}[!th]
\begin{minipage}[!bp]{0.35\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stack_z1.pdf}
%\includegraphics[width=\textwidth]{f03.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\includegraphics[width=\textwidth]{Figures/fig_monte.pdf}
%\includegraphics[width=\textwidth]{f07.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of 
Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
data. The model has a smaller dispersion than the data by two times the modeling error.
}
\label{fig:monte}
\end{minipage}%
\hspace{0.5in}
\begin{minipage}[!bp]{0.55\textwidth}
\includegraphics[width=\textwidth]{Figures/fig_stacks_fg.pdf}
%\includegraphics[width=\textwidth]{f04.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{minipage}
\end{figure*}

@@

@@

Since \ion{C}{2} systems arise in optically thick absorbers, we may adopt the clustering analysis 
results of QPQ6. In the absence of clustering, the expected number of absorbers per unit redshift 
interval for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\ell_{\rm IGM}^{\rm LLS}(z)\approx1.05((1+z)/(1+2.5))^{2.1}$, 
$\ell_{\rm IGM}^{\rm SLLS}(z)\approx0.44((1+z)/(1+2.5))^{2.1}$, and 
$\ell_{\rm IGM}^{\rm DLA}(z)\approx0.2((1+z)/(1+2.5))^{2.1}$. The quasar-absorber correlation 
functions for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\xi_{\rm QA}^{\rm LLS}(r)=(r/(12.5\,h^{-1}\,{\rm Mpc}))^{-1.68}$, 
$\xi_{\rm QA}^{\rm SLLS}(r)=(r/(14.0\,h^{-1}\,{\rm Mpc}))^{-1.68}$, and 
$\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
For each quasar pair, we calculate the expected number of all optically thick absorbers within 
$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
$z_{\rm fg}$. Then we generate 1000 mock sightlines. The number of absorbers for each mock 
spectrum is randomly selected from a Poisson distribution with mean equal to the expected number 
calculated as above. The absorbers are randomly assigned Hubble velocities, with a probability 
distribution according to the quasar-absorber correlation functions. The absorbers are randomly 
assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
amplitude of the stack of the observational data. We find that a rest equivalent width of 
0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
insensitive to the assumed equivalent width or line profile for one absorber. In 
Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
The resulting stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, 
which is smaller than the intrinsic dispersion in the data by two times the $1\sigma$ modeling 
error. We also test for the sensitivity of this 
measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
fact intercept more than one optically thick absorber. We double the number of absorbers for each 
mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
velocity of $\approx280\,{\rm km\,s^{-1}}$ is required. Thus, the observed velocity width suggests 
a hint of dynamical processes in addition to gravitational motions and Hubble flows.

@@

In conclusion, we observe large and positively skewed velocity fields in absorption, of metal ions 
in the CGM of $z\sim2$ massive galaxies hosting quasars. We interpret the results as evidence that 
the detected gas is outflowing, and that the quasars either shine anisotropically or 
intermittently.

>>>>

\title{Quasars Probing Quasars IX. Probing the Circumgalactic Flows of Quasars [v1.4]}

@@

\begin{abstract}
Absorption-line analysis of the circumgalactic medium has traditionally been limited by the 
difficulty to distinguish between inflows and outflows. We examine the flows of gas in the 
environments of massive galaxies hosting quasars at $z\sim2$. We employ 115 projected quasar pairs 
to study the circumgalactic gas of the foreground quasars in absorption. The foreground quasars 
have precise redshift measurements with uncertainty $<400\,{\rm km\,s^{-1}}$. We stack the 
background quasar spectra at the foreground quasar's systemic redshift. The mean absorption in 
\ion{C}{2}, \ion{C}{4}, and \ion{Mg}{2} show large velocity widths, and have velocity 
centroids that show a small positive offset relative to the systemic. We argue that a possible 
explanation to the observed velocity fields is outflowing gas combined with anisotropic or 
intermittent ionizing radiation of the quasars. 
\end{abstract}

@@

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_stack_z1.pdf}
%\includegraphics[width=2.5in]{f03.pdf}
\caption{Mean stack at \ion{Mg}{2}\,2796, for a lower redshift sample of quasar pairs at 
$z\sim0.9$. Line-style coding is the same as in Figure~\ref{fig:stacks_and_fits}. The centroid is 
approximately $0\,{\rm \,km\,s^{-1}}$, and the absorption is weaker than the main QPQ9 sample. 
}
\label{fig:stack_z1}
\end{figure}

\begin{figure}
\includegraphics[width=3.4in]{Figures/fig_stacks_fg.pdf}
%\includegraphics[width=3.4in]{f04.pdf}
\caption{Mean stacks of the foreground quasar spectra at \ion{C}{2}\,1334, \ion{C}{4}\,1548, and 
\ion{Mg}{2}\,2796 for the QPQ9 sample. For \ion{C}{2} and \ion{Mg}{2}, there is no evidence of 
excess absorption near $z_{\rm fg}$. The stack for \ion{C}{4}, which include line-of-sight 
absorbers at all distances, shows a large, blueshifted mean velocity field.
}
\label{fig:stacks_fg}
\end{figure}

@@

\begin{figure}
\includegraphics[width=2.5in]{Figures/fig_monte.pdf}
%\includegraphics[width=2.5in]{f07.pdf}
\caption{The same \ion{C}{2} mean stack shown in the first panel of 
Figure~\ref{fig:stacks_and_fits} is shown in thick, black, and the Gaussian absorption model to 
the data is shown in thin, blue. In thin, green, we overplot the Gaussian absorption model of the 
Monte Carlo simulations generated from a purely clustering argument. The model from clustering 
analysis is multiplied to the pseudo-continuum level of the stack of the observational data, 
shifted to the centroid of the stack of the data, and broadened by the mean redshift error in the 
data. The model has a smaller dispersion than the data by two times the modeling error.
}
\label{fig:monte}
\end{figure}

@@

Since \ion{C}{2} systems arise in optically thick absorbers, we may adopt the clustering analysis 
results of QPQ6. In the absence of clustering, the expected number of absorbers per unit redshift 
interval for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\ell_{\rm IGM}^{\rm LLS}(z)\approx1.05((1+z)/(1+2.5))^{2.1}$, 
$\ell_{\rm IGM}^{\rm SLLS}(z)\approx0.44((1+z)/(1+2.5))^{2.1}$, and 
$\ell_{\rm IGM}^{\rm DLA}(z)\approx0.2((1+z)/(1+2.5))^{2.1}$. The quasar-absorber correlation 
functions for Lyman limit systems, super Lyman limit systems, and damped Ly$\alpha$ systems are 
respectively $\xi_{\rm QA}^{\rm LLS}(r)=(r/(12.5\,h^{-1}\,{\rm Mpc}))^{-1.68}$, 
$\xi_{\rm QA}^{\rm SLLS}(r)=(r/(14.0\,h^{-1}\,{\rm Mpc}))^{-1.68}$, and 
$\xi_{\rm QA}^{\rm DLA}(r)=(r/(3.9\,h^{-1}\,{\rm Mpc}))^{-1.6}$. 
For each quasar pair, we calculate the expected number of all optically thick absorbers within 
$\pm3000\,{\rm km\,s^{-1}}$ at a distance $R_\perp$ from the foreground quasar and at 
$z_{\rm fg}$. Then we generate 1000 mock sightlines. The number of absorbers for each mock 
spectrum is randomly selected from a Poisson distribution with mean equal to the expected number 
calculated as above. The absorbers are randomly assigned Hubble velocities, with a probability 
distribution according to the quasar-absorber correlation functions. The absorbers are randomly 
assigned additional peculiar velocities drawn from a normal distribution with mean equal to 
$0\,{\rm km\,s^{-1}}$ and scatter equal to $\sigma_{\rm 1D}$. For each absorber, we 
assume a rest equivalent width for \ion{C}{2} and a Gaussian absorption profile. We repeat the 
above procedure for all 34 quasar pairs, and create a mean stack of the 34000 mock spectra 
generated. We fit a Gaussian absorption profile multiplied to a constant continuum level to model 
the stack of mock spectra. We adjust the rest equivalent width adopted for the \ion{C}{2} 
absorbers until the ampltiude of the best-fit Gaussian of the stack of mock spectra matches the 
amplitude of the stack of the observational data. We find that a rest equivalent width of 
0.6\,\AA\ well reproduces the amplitude, and the dispersion of the Gaussian absorption model is 
insensitive to the assumed equivalent width or line profile for one absorber. In 
Figure~\ref{fig:monte}, we show a comparison of the observational data stack and the Gaussian 
absorption model of the Monte Carlo simulations. In the figure, the Gaussian absorption model is 
broadened by the mean redshift error by adding it in quadrature to the dispersion in the model. 
The resulting stack of mock spectra has a $1\sigma$ dispersion of $\approx240\,{\rm km\,s^{-1}}$, 
which is smaller than the intrinsic dispersion in the data by two times the $1\sigma$ modeling 
error. We also test for the sensitivity of this 
measured dispersion to the correlation functions adopted. The QPQ6 clustering analysis is 
performed on only the strongest absorber near $z_{\rm fg}$, and a low $R_\perp$ sightline may in 
fact intercept more than one optically thick absorber. We double the number of absorbers for each 
mock sightline, and find the measured dispersion only increases by several ${\rm km\,s^{-1}}$. 
In order to recover an intrinsic dispersion of $317\textendash352\,{\rm km\,s^{-1}}$, a peculiar 
velocity of $\approx285\,{\rm km\,s^{-1}}$ is required. The observed velocity width thus suggests 
a hint of dynamical processes in addition to gravitational motions and Hubble flows.

@@

In conclusion, we observe large and positively skewed velocity fields in absorption, of metal ions 
in the CGM of $z\sim2$ massive galaxies hosting quasars. We argue that the velocity fields can be 
explained if the detected gas is outflowing, and the quasars either shine anisotropically or 
intermittently.
